Exploratory Analysis

### 2021-11-30 eda-h.Rmd

@@

>>>>

When looking at age and HeartDisease there seems to be a clear difference between the two means , which can also be seem in the sex category.

@@

```{r}
p1 <- ggplot(train,aes(x=Oldpeak,y=HeartDisease))+ geom_boxplot()+coord_flip()

p2 <-ggplot(train,aes(x=ExerciseAngina,fill=HeartDisease))+ geom_bar(position = "dodge")

p3 <-ggplot(train,aes(x=ST_Slope,fill=HeartDisease))+ geom_bar(position = "dodge")

ggarrange(p1,p2,p3)
```
